---
title: "Final_Project"
author: "Haw-Jan Hwang"
date: "October 14, 2019"
output:
  word_document: default
  html_document: default
---
# Packages
```{r set environment,include=FALSE, message=FALSE, warning=FALSE}
if(!require ("ggplot2")) install.packages("ggplot2")
if(!require ("corrplot")) install.packages("corrplot")
if(!require ("corrgram")) install.packages("corrgram")
if(!require ("gridExtra")) install.packages("gridExtra")
if(!require ("e1071")) install.packages("e1071")
if(!require ("randomForest")) install.packages("randomForest")
if(!require ("tidyverse")) install.packages("tidyverse")
if(!require ("dplyr")) install.packages("dplyr")
if(!require ("caTools")) install.packages("caTools")
if(!require ("caret")) install.packages("caret")
if(!require ("MASS")) install.packages("MASS")
if(!require ("rpart")) install.packages("rpart")
if(!require ("rpart.plot")) install.packages("rpart.plot")
if(!require ("MASS")) install.packages("MASS")
if(!require ("fmsb")) install.packages("fmsb")
if(!require ("plotly")) install.packages("plotly")

library(randomForest)
library(tidyverse)
library(e1071)
library(ggplot2)
library(corrplot)
library(corrgram)
library(gridExtra)
library(dplyr)
library(rpart)
library(caTools)
library(caret)
library(rpart.plot)
library(MASS)
library(fmsb)
library(plotly)

```
# Import Data
There are total 20 columns and 3338 rows and most of the features are numeric data
```{r}
df = read.csv('SkillCraft.csv')
str(df)
```
# Attribute Information
1. GameID: Unique ID number for each game (integer)
2. LeagueIndex: Bronze, Silver, Gold, Platinum, Diamond, Master, GrandMaster, and Professional leagues coded 1-7 (Ordinal)
3. Age: Age of each player (integer)
4. HoursPerWeek: Reported hours spent playing per week (integer)
5. TotalHours: Reported total hours spent playing (integer)
6. APM: Action per minute (continuous)
7. SelectByHotkeys: Number of unit or building selections made using hotkeys per timestamp (continuous)
8. AssignToHotkeys: Number of units or buildings assigned to hotkeys per timestamp (continuous)
9. UniqueHotkeys: Number of unique hotkeys used per timestamp (continuous)
10. MinimapAttacks: Number of attack actions on minimap per timestamp (continuous)
11. MinimapRightClicks: number of right-clicks on minimap per timestamp (continuous)
12. NumberOfPACs: Number of PACs per timestamp (continuous) (A PAC is when one changes screen location and performs 1+ actions before changing screen location again to repeat.)
13. GapBetweenPACs: Mean duration in milliseconds between PACs (continuous)
14. ActionLatency: Mean latency from the onset of a PACs to their first action in milliseconds (continuous)
15. ActionsInPAC: Mean number of actions within each PAC (continuous)
16. TotalMapExplored: The number of 24x24 game coordinate grids viewed by the player per timestamp (continuous)
17. WorkersMade: Number of SCVs, drones, and probes trained per timestamp (continuous)
18. UniqueUnitsMade: Unique unites made per timestamp (continuous)
19. ComplexUnitsMade: Number of ghosts, infestors, and high templars trained per timestamp (continuous)
20. ComplexAbilitiesUsed: Abilities requiring specific targeting instructions used per timestamp (continuous)

# Data Summary
From the code below, we can see the preliminary summary of all the features.
```{r}
summary(df)
```
From the summary above and the graph, we can see there is 1 outlier (TotalHours): max is 100000 but the mean and the mediarn are much less (500, 960)
```{r}
total_hours = ggplot(data=df,aes(x=TotalHours)) + ggtitle('Total Hours Count') +geom_histogram(bins=50)
print(total_hours)
```
# Data Cleaning
I remove the outlier and the GameID feature.
```{r}
df = df[,-1]
df = df[df$TotalHours!=1000000,]
new_total_hours = ggplot(data=df,aes(x=TotalHours)) + ggtitle('Total Hours Count after removed outlier') + geom_histogram(bins=100)
print(new_total_hours)
```
Transform The LeagueName feature into Categorical variable
```{r}
league = function(x){
    if (x==1) {return('Bronze')}
    else if (x==2) {return('Silver')}
    else if (x==3) {return('Gold')}
    else if (x==4) {return('Platinum')}
    else if (x==5) {return('Diamond')}
    else if (x==6) {return('Master')}
    else {return('Grand Master')}
}
df$LeagueName = sapply(df$LeagueIndex,league)
```


```{r}
df <- na.omit(df)
```

# Feature Group 1
```{r}
group1<-df %>% group_by(LeagueIndex) %>% select(Age, HoursPerWeek, TotalHours, APM, ActionLatency, GapBetweenPACs, ActionsInPAC) %>% summarise(avg_age = mean(Age), avg_Hours = mean(HoursPerWeek), avgTotalHours = mean(TotalHours), avg_APM = mean(APM), avg_actionLatency = mean(ActionLatency), avg_GapPacs= mean(GapBetweenPACs), avg_actionPac = mean(ActionsInPAC))
```
# Feature Group 2
```{r}
group2<-df %>% group_by(LeagueIndex) %>% select(SelectByHotkeys,AssignToHotkeys,UniqueHotkeys,MinimapAttacks, MinimapRightClicks,NumberOfPACs, TotalMapExplored, WorkersMade, UniqueUnitsMade, ComplexUnitsMade, ComplexAbilitiesUsed) %>% summarise(avg_selectHotKeys = mean(SelectByHotkeys), avg_assignHotKeys = mean(AssignToHotkeys), avg_minimapAttacks = mean(MinimapAttacks),avg_minimapRightClicks = mean(MinimapRightClicks), avg_numPacs = mean(NumberOfPACs), avg_worker = mean(WorkersMade), avg_complexUnit = mean(ComplexUnitsMade), avg_complexAbilities = mean(ComplexAbilitiesUsed))
```

```{r}
maxGr1<-c(50,50,1750,200,100,100,10)
minGr1<-rep(0,7)
maxGr2<-c(.01,.01,.01,.01,.01,.01,.01,.01)
minGr2<-rep(0,11)

```

# Grand Master
```{r}
gr1GML<-rbind(maxGr1,minGr1,group1[7,2:8])
gr2GML<-rbind(maxGr2,minGr2,group2[7,2:9])

op <- par(mar=c(1, 2, 2, 1),mfrow=c(1, 2))
radarchart( gr1GML  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.9,0.5,0.5,0.9) , pfcol=rgb(0.9,0.5,0.5,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,2000,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
radarchart( gr2GML  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.9,0.5,0.5,0.9) , pfcol=rgb(0.9,0.5,0.5,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,.1,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )

par(op)
```
# Master
```{r}
gr1ML<-rbind(maxGr1,minGr1,group1[6,2:8])
gr2ML<-rbind(maxGr2,minGr2,group2[6,2:9])
op <- par(mar=c(1, 2, 2, 1),mfrow=c(1, 2))
radarchart( gr1ML  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.9,0.5,0.5,0.9) , pfcol=rgb(0.9,0.5,0.5,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,2000,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
radarchart( gr2ML  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.9,0.5,0.5,0.9) , pfcol=rgb(0.9,0.5,0.5,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,.1,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
```
# Diamond
```{r}
gr1DL<-rbind(maxGr1,minGr1,group1[5,2:8])
gr2DL<-rbind(maxGr2,minGr2,group2[5,2:9])
op <- par(mar=c(1, 2, 2, 1),mfrow=c(1, 2))
radarchart( gr1DL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,2000,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
radarchart( gr2DL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,.1,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
```
# Platinum
```{r}
gr1PL<-rbind(maxGr1,minGr1,group1[4,2:8])
gr2PL<-rbind(maxGr2,minGr2,group2[4,2:9])
op <- par(mar=c(1, 2, 2, 1),mfrow=c(1, 2))
radarchart( gr1DL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,2000,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
radarchart( gr2DL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,.1,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
```
# Gold
```{r}
gr1GL<-rbind(maxGr1,minGr1,group1[3,2:8])
gr2GL<-rbind(maxGr2,minGr2,group2[3,2:9])
op <- par(mar=c(1, 2, 2, 1),mfrow=c(1, 2))
radarchart( gr1GL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.9,0.9) , pfcol=rgb(0.2,0.5,0.9,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,2000,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
radarchart( gr2GL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.9,0.9) , pfcol=rgb(0.2,0.5,0.9,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,.1,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
```
# Silver
```{r}
gr1SL<-rbind(maxGr1,minGr1,group1[2,2:8])
gr2SL<-rbind(maxGr2,minGr2,group2[2,2:9])
op <- par(mar=c(1, 2, 2, 1),mfrow=c(1, 2))
radarchart( gr1SL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.9,0.9) , pfcol=rgb(0.2,0.5,0.9,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,2000,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
radarchart( gr2SL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.9,0.9) , pfcol=rgb(0.2,0.5,0.9,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,.1,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
```
# Bronze
```{r}
gr1BL<-rbind(maxGr1,minGr1,group1[1,2:8])
gr2BL<-rbind(maxGr2,minGr2,group2[1,2:9])
op <- par(mar=c(1, 2, 2, 1),mfrow=c(1, 2))
radarchart( gr1BL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.9,0.9) , pfcol=rgb(0.2,0.5,0.9,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,2000,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
radarchart( gr2BL  , axistype=2 , 
    #custom polygon
     pcol=rgb(0.2,0.5,0.9,0.9) , pfcol=rgb(0.2,0.5,0.9,0.5) , plwd=4 , 
     #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,.1,5), cglwd=0.8,
    #custom labels
     vlcex=0.6 
     )
```

# Correlation plot
Check if there are features correlated with each other.
From below, we can see the ActionLatency and GapBetweenPACs have high correlation with multiple variable.
```{r}
num.cols = sapply(df, is.numeric)
cor.data = cor(df[,num.cols])
corrPLOT = corrplot(cor.data,method='ellipse',  title="Heat Map")
```

# Data Exploration
Our target variable is LeagueName, see different class of LeagueName have what features, help us to classificate future data.
1. Start from variable Action Latency and Gap Between PACs, because these two have high correlation
```{r}
# ActionLatency in different League
actionLatVsLeague<-ggplot(data=df,aes(x=factor(LeagueIndex),y= ActionLatency)) + 
geom_boxplot()  + ggtitle('Action Latency in different League')+
xlab('League Index') + ylab('Action Latency')
print(actionLatVsLeague)
```

```{r}
# GapBetweenPACs in different League
gapPacVsLeague<-ggplot(data=df,aes(x=factor(LeagueIndex),y= GapBetweenPACs)) + 
geom_boxplot() + ggtitle('Gap Between PACs in different League')+
xlab('League Index') + ylab('Gap Between PACs')

print(gapPacVsLeague)
```
From the two graphs above we can see that these 2 variables have very simillar feature, consider to use feature selection in the future. 

```{r}
# Weekly time playing in different League
hourWeekVsLeague<-ggplot(data=df,aes(x=factor(LeagueIndex),y= HoursPerWeek)) + 
geom_boxplot()  + ggtitle('Weekly time playing in different League')+
xlab('League Index') + ylab('HoursPerWeek')
print(hourWeekVsLeague)
```

```{r}
ageVsLeague<-ggplot(data=df,aes(x=factor(LeagueIndex),y= Age)) + 
geom_boxplot()+ ggtitle('Age in different League')+
xlab('League Index') + ylab('Age')
print(ageVsLeague)
```

```{r}
uniqueUnitsMadeVsLeague<-ggplot(data=df,aes(x=factor(LeagueIndex),y= UniqueUnitsMade)) + 
geom_boxplot() + ggtitle('Unique unit makes in different League')+
xlab('League Index') + ylab('Unique Units Made')
print(uniqueUnitsMadeVsLeague)
```
```{r}
complexUnitsMadeVsLeague<-ggplot(data=df,aes(x=factor(LeagueIndex),y= ComplexUnitsMade)) + 
geom_boxplot()  + ggtitle('Complex unit made in different League')+
xlab('League Index') + ylab('Complex Units Made')
print(complexUnitsMadeVsLeague)
```
# Hypotheses after Data Exploration
It looks like the age is not very sensitive to different class; GapBetweenPACs and ActionLatency are very similar, maybe I should try feature selection model(Lasso Regression); Weekly time playing might be a very strong variable.

# Train Test Split
1. Split data into train, test
```{r}
set.seed(123)
df2<-subset( df, select = -c(LeagueIndex) )
split<-sample.split(df2$LeagueName,SplitRatio=0.7)
train<-subset(df2,split==T)
test<-subset(df2,split==F)
```

# Decision Tree
```{r}
tree <- rpart(LeagueName ~ ., method='class',data = train)
print(tree$variable.importance)
```
```{r}
prp(tree)
```


# LDA
```{r}
lda.pred=lda(LeagueName~.,data=train)
lda.pred


```
```{r}
ldatest=predict(lda.pred,test)
#ldatest$x
table(ldatest$class,test$LeagueName) 
```
```{r}
z <- data.frame(ldatest$x, label=test$LeagueName)

ggplot(z[z$label=='Grand Master' | z$label=="Bronze",], aes(LD1,LD2))+geom_point(aes(col=label))
```
```{r}
mean(ldatest$class==test$LeagueName)
```

# QDA
```{r}
qda.pred=qda(LeagueName~.,data=train)
qda.pred
```

```{r}
qdatest=predict(qda.pred,test)

table(qdatest$class,test$LeagueName) 
```

```{r}
mean(qdatest$class==test$LeagueName)
```

# Random Forest
```{r}
train$LeagueName = factor(train$LeagueName)
rf.model<-randomForest(LeagueName ~ . , data = train,importance = TRUE)
print(rf.model)
```
```{r}
predictionRF<-as.data.frame(predict(rf.model,test))
colnames(predictionRF)<-c('res')
test$LeagueName <- as.factor(test$LeagueName)
confusionMatrix(predictionRF$res,test$LeagueName)
```

# SVM linear B4 tune
```{r}
svm_linear<-svm(LeagueName~., data=train, kernel='linear', cost=0.01)
summary(svm_linear)

# Prediction
pred_train_linear <- svm_linear$fitted
pred_test_linear <- predict(svm_linear,test)

# Error
conf_mtrx_train <- confusionMatrix(train$LeagueName,pred_train_linear)
cat("Linear train error rate(B4 tuned):",1-conf_mtrx_train$overall[1],"\n\n")

conf_mtrx_test <- confusionMatrix(test$LeagueName,pred_test_linear)
cat("Linear test error rate(B4 tuned):",1-conf_mtrx_test$overall[1],"\n\n")

```
```{r}
print(conf_mtrx_train)
print(conf_mtrx_test)
```

# SVM radial B4 tune
```{r}
svm_radial<-svm(LeagueName~., data=train, kernel='radial', cost=0.01)
summary(svm_radial)

# Prediction
pred_train_radial <- svm_radial$fitted
pred_test_radial <- predict(svm_radial,test)

# Error
conf_mtrx_train <- confusionMatrix(train$LeagueName,pred_train_radial)
cat("Radial train error rate(B4 tuned):",1-conf_mtrx_train$overall[1],"\n\n")

conf_mtrx_test <- confusionMatrix(test$LeagueName,pred_test_radial)
cat("Radial test error rate(B4 tuned):",1-conf_mtrx_test$overall[1],"\n\n")

```
```{r}
print(conf_mtrx_train)
print(conf_mtrx_test)
```

# SVM linear after tune
```{r}
# Tuned model
tune_linear <- tune(svm, LeagueName~., data=train, kernel='linear', range = list(cost=seq(0.01,2.5,0.5)))

# Prediction
pred_train_linear_tuned <- tune_linear$best.model$fitted
pred_test_linear_tuned <- predict(tune_linear$best.model,test)

# Error
conf_mtrx_train_tuned <- confusionMatrix(train$LeagueName,pred_train_linear_tuned)
cat("Radial tuned train error rate(after tuned):",1-conf_mtrx_train_tuned$overall[1],"\n\n")

conf_mtrx_test_tuned <- confusionMatrix(test$LeagueName,pred_test_linear_tuned)
cat("Radial tuned test error rate(after tuned):",1-conf_mtrx_test_tuned$overall[1])
```

```{r}
print(conf_mtrx_train_tuned)
print(conf_mtrx_test_tuned)
```

# SVM radial after tune
```{r}
# Tuned model
tune_radial <- tune(svm, LeagueName~., data=train, kernel='radial', range = list(cost=seq(0.01,10,0.1)))

# Prediction
pred_train_radial_tuned <- tune_radial$best.model$fitted
pred_test_radial_tuned <- predict(tune_radial$best.model,test)

# Error
conf_mtrx_train_tuned <- confusionMatrix(train$LeagueName,pred_train_radial_tuned)
cat("Radial tuned train error rate(after tuned):",1-conf_mtrx_train_tuned$overall[1],"\n\n")

conf_mtrx_test_tuned <- confusionMatrix(test$LeagueName,pred_test_radial_tuned)
cat("Radial tuned test error rate(after tuned):",1-conf_mtrx_test_tuned$overall[1])
```

```{r}
print(conf_mtrx_train_tuned)
print(conf_mtrx_test_tuned)
```



# Three Class
```{r}
makeLeague<-function(x){
  if(x>=1 & x<=3) {return('LOW')}
  else if(x>3 & x<6) {return('MID')}
  else if(x>=6) {return('HIGH')}
}
df$League3<-sapply(df$LeagueIndex,makeLeague)
```

```{r}
set.seed(123)
df3<-subset( df, select = -c(LeagueIndex,LeagueName) )
split<-sample.split(df3$League3,SplitRatio=.7)
train<-subset(df3,split==T)
test<-subset(df3,split==F)
```

```{r}
tree <- rpart(League3 ~ ., method='class',data = train)
print(tree$variable.importance)
```
```{r}
prp(tree)
```
# LDA with 3 class
```{r}
lda.pred=lda(League3~.,data=train)
lda.pred
```

```{r}
ldatest=predict(lda.pred,test)

table(ldatest$class,test$League3) 
```
```{r}
z <- data.frame(ldatest$x, label=test$League3)

ggplot(z[z$label=='HIGH' | z$label=="MID" | z$label=="LOW",], aes(LD1,LD2))+geom_point(aes(col=label))
```
```{r}
mean(ldatest$class==test$League3)
```
# QDA with 3 class
```{r}
qda.pred=qda(League3~.,data=train)
qda.pred
```
```{r}
qdatest=predict(qda.pred,test)

table(qdatest$class,test$League3)
```
```{r}
mean(qdatest$class==test$League3)
```
# Random Forest with 3 class
```{r}
train$League3 = factor(train$League3)
rf.model<-randomForest(League3 ~ . , data = train,importance = TRUE)
print(rf.model)
```

```{r}
predictionRF<-as.data.frame(predict(rf.model,test))
colnames(predictionRF)<-c('res')
test$League3 <- as.factor(test$League3)
confusionMatrix(predictionRF$res,test$League3)
```
# SVM linear B4 tuned (3 class)
```{r}
svm_linear<-svm(League3~., data=train, kernel='linear', cost=0.01)
summary(svm_linear)

# Prediction
pred_train_linear <- svm_linear$fitted
pred_test_linear <- predict(svm_linear,test)

# Error
conf_mtrx_train <- confusionMatrix(train$League3,pred_train_linear)
cat("Linear train error rate(B4 tuned):",1-conf_mtrx_train$overall[1],"\n\n")

conf_mtrx_test <- confusionMatrix(test$League3,pred_test_linear)
cat("Linear test error rate(B4 tuned):",1-conf_mtrx_test$overall[1],"\n\n")

```

```{r}
print(conf_mtrx_train)
print(conf_mtrx_test)
```
# SVM linear after tuned (3 class)
```{r}
# Tuned model
tune_linear <- tune(svm, League3~., data=train, kernel='linear', range = list(cost=seq(0.01,2.5,0.5)))

# Prediction
pred_train_linear_tuned <- tune_linear$best.model$fitted
pred_test_linear_tuned <- predict(tune_linear$best.model,test)

# Error
conf_mtrx_train_tuned <- confusionMatrix(train$League3,pred_train_linear_tuned)
cat("Radial tuned train error rate(after tuned):",1-conf_mtrx_train_tuned$overall[1],"\n\n")

conf_mtrx_test_tuned <- confusionMatrix(test$League3,pred_test_linear_tuned)
cat("Radial tuned test error rate(after tuned):",1-conf_mtrx_test_tuned$overall[1])
# SVM radial B4 tune (3 class)
```
```{r}
print(conf_mtrx_train_tuned)
print(conf_mtrx_test_tuned)
```

# SVM radial b4 tuned (3 class)
```{r}
svm_radial<-svm(League3~., data=train, kernel='radial', cost=0.01)
summary(svm_radial)

# Prediction
pred_train_radial <- svm_radial$fitted
pred_test_radial <- predict(svm_radial,test)

# Error
conf_mtrx_train <- confusionMatrix(train$League3,pred_train_radial)
cat("Radial train error rate(B4 tuned):",1-conf_mtrx_train$overall[1],"\n\n")

conf_mtrx_test <- confusionMatrix(test$League3,pred_test_radial)
cat("Radial test error rate(B4 tuned):",1-conf_mtrx_test$overall[1],"\n\n")
```
```{r}
print(conf_mtrx_train)
print(conf_mtrx_test)
```

# SVM radial after tuned (3 class)
```{r}

# Tuned model
tune_radial <- tune(svm, League3~., data=train, kernel='radial', range = list(cost=seq(0.01,10,0.1)))

# Prediction
pred_train_radial_tuned <- tune_radial$best.model$fitted
pred_test_radial_tuned <- predict(tune_radial$best.model,test)

# Error
conf_mtrx_train_tuned <- confusionMatrix(train$League3,pred_train_radial_tuned)
cat("Radial tuned train error rate(after tuned):",1-conf_mtrx_train_tuned$overall[1],"\n\n")

conf_mtrx_test_tuned <- confusionMatrix(test$League3,pred_test_radial_tuned)
cat("Radial tuned test error rate(after tuned):",1-conf_mtrx_test_tuned$overall[1])

```

```{r}
print(conf_mtrx_train_tuned)
print(conf_mtrx_test_tuned)
```











